Measurement of total hadronic differential cross sections in the LArIAT experiment

### 2018-04-10 Chapter-1/1-Theory.tex
s

Historically, neutrino interactions with the nucleus are divided into three categories as a function of increasing neutrino energy: quasi elastic, resonant and deep inelastic scattering.
All current and forthcoming oscillation experiments live in
the 0.1-10 GeV transition region, which encompasses the energy where the quasi-elastic neutrino-nucleus interaction transitions into resonance scattering and the energy  resonance scattering  transitions in to deep inelastic scattering. 
\textcolor{red}{PLOT}

%%%%%%%%%%%%%%%%%%%%%%%%  
\textbf{Quasi-elastic scattering}
Quasi-elastic (QE) scattering is the dominant neutrino interaction for neutrino energies less than ? 1 GeV and represents a large fraction of the signal samples in many neutrino oscillation experiments. Historically, neutrino (antineutrino) quasi-elastic scattering refers to the process $\nu_\mu n \rightarrow \mu^- p$ and ($\bar\nu_\mu p \rightarrow \mu^+ n$) where a charged lepton and single nucleon are ejected in the elastic interaction of a neutrino (or antineutrino) with a nucleon in the target material. This is the final state one would strictly observe, for example, in scattering off of a free nucleon target. %% ADD DIFFERENCES WITH HEAVIER TARGETS
In many of these initial measurements of the neutrino QE cross section, bubble chamber experiments employed light targets (H2 or D2) and required both the detection of the final state muon and single nucleon; thus the final state was clear and elastic kinematic conditions could be verified. The situation is more complicated, of course, for heavier nuclear targets. In this case, nuclear effects can impact the size and shape of the cross section as well as the final state kinematics and topology. Due to intra-nuclear hadron rescattering and the possible effects of correlations between target nucleons, additional nucleons may be ejected in the final state; hence, a QE interaction on a nuclear target does not always imply the ejection of a single nucleon. 
One therefore needs to take some care in defining what one means by neutrino QE scattering when scattering off targets heavier than H2 or D2.

Fig. 49.2 displays the current status of existing measurements of $\nu_\mu$ and $\bar\nu_\mu$ QE scattering cross sections as a function of neutrino energy. In this plot, and all others in this review, the prediction from a representative neutrino event generator (NUANCE) [46] provides a theoretical comparator. MiniBooNE XS enanchement Such an enhancement is believed to be due to the presence of correlations between target nucleons in the nucleus. As a result, the impact of such nuclear effects on neutrino QE scattering has recently been the subject of intense experimental and theoretical scrutiny with potential implications on event rates, nucleon emission, neutrino energy reconstruction, and neutrino/antineutrino ratios. 
Experiments such as ArgoNeuT have begun to provide the first measurements of proton multiplicities in neutrino-argon QE scattering [4,48], a critical ingredient in understanding the hadronic side of these interactions and final state effects.

>>>>

Historically, neutrino interactions with the nucleus in the few GeV region are divided into three categories as a function of increasing neutrino energy: quasi elastic, resonant and deep inelastic scattering. In this simple framework, neutrino (antineutrino) quasi-elastic scattering refers to the process $\nu_\mu n \rightarrow \mu^- p$ and ($\bar\nu_\mu p \rightarrow \mu^+ n$) where a charged lepton and single nucleon are ejected in the elastic interaction of a neutrino (or antineutrino) with a nucleon in the target material. Resonant scattering refers to an inelastic collision producing a nucleon excited state ($\Delta$,N*). The excited resonance quickly decays, most often to a nucleon and single-pion final state. Deep inelastic refers to the head on collision between the neutrino and a parton inside the nucleon, producing a subsequent hadronization.
This simple model

All current and forthcoming oscillation experiments live in
the 0.1-10 GeV transition region, which encompasses the energy where the quasi-elastic neutrino-nucleus interaction transitions into resonance scattering and the energy  where resonance scattering  transitions in to deep inelastic scattering.

\textcolor{red}{PLOT}
more schematic: what 
\begin{enumerate}
\item QE
\item Resonance
\item DIS
\end{enumerate}

Complications
%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Quasi-elastic scattering}
Quasi-elastic (QE) scattering is the dominant neutrino interaction for neutrino energies less than $\sim1$ GeV and represents a large fraction of the signal samples in many neutrino oscillation experiments. Historically, neutrino (antineutrino) quasi-elastic scattering refers to the process $\nu_\mu n \rightarrow \mu^- p$ and ($\bar\nu_\mu p \rightarrow \mu^+ n$) where a charged lepton and single nucleon are ejected in the elastic interaction of a neutrino (or antineutrino) with a nucleon in the target material.

This is the final state one would strictly observe, for example, in scattering off of a free nucleon target. %% ADD DIFFERENCES WITH HEAVIER TARGETS
The situation is more complicated, of course, for heavier nuclear targets. In this case, nuclear effects can impact the size and shape of the cross section as well as the final state kinematics and topology. Due to intra-nuclear hadron rescattering and the possible effects of correlations between target nucleons, additional nucleons may be ejected in the final state; hence, a QE interaction on a nuclear target does not always imply the ejection of a single nucleon. 
One therefore needs to take some care in defining what one means by neutrino QE scattering when scattering off targets heavier than H2 or D2. 
Fig. 49.2 displays the current status of existing measurements of $\nu_\mu$ and $\bar\nu_\mu$ QE scattering cross sections as a function of neutrino energy. In this plot, and all others in this review, the prediction from a representative neutrino event generator (NUANCE) [46] provides a theoretical comparator. MiniBooNE XS enanchement Such an enhancement is believed to be due to the presence of correlations between target nucleons in the nucleus. As a result, the impact of such nuclear effects on neutrino QE scattering has recently been the subject of intense experimental and theoretical scrutiny with potential implications on event rates, nucleon emission, neutrino energy reconstruction, and neutrino/antineutrino ratios. 
Experiments such as ArgoNeuT have begun to provide the first measurements of proton multiplicities in neutrino-argon QE scattering [4,48], a critical ingredient in understanding the hadronic side of these interactions and final state effects.
